---
title: "Flow Analysis Pipeline"
author: "Domenic Abbondanza & Lexi Cassano"
date: "`r Sys.Date()`"
output:
    html_document:
        df_print: tibble
        highlight: tango
        theme: united
        toc: yes
        toc_float:
            collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This code is for use in analyzing multi-parameter flow cytometry data. Data is treated as single cell data. Code uses the Spectre R package (https://immunedynamics.io/spectre/simple-discovery/) by Thomas Myles Ashhurst, Felix Marsh-Wakefield, and Givanna Putri. Code is written by Domenic Abbondanza and Lexi Cassano.

# Set up

## Install and load libraries
### Install libraries
Only run this chunk/code if libraries need to be installed.
```{r install_libraries, eval=FALSE}
install.packages("devtools")
library(devtools)
install.packages("tidyverse")
devtools::install_github("https://github.com/ImmuneDynamics/spectre")
```

### Load libraries
This code must be run every session
```{r load_libraries}
library(devtools)
library(tidyverse)
library(colorblindr)
library(paletteer)
library(utils)
library(stringi)
library(stringr)
library(knitr)
library(rmarkdown)
library(Spectre)
```